---
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_width: 25
    fig_height: 25
classoption: landscape
geometry: margin=2cm
params:
  pc: 0.8
  dpc: 0.98
  file1: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AKFM094700-HA.csv
  file2: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AAFM094704-HA.csv
  file3: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AVFM094684-HA.csv
  path: '~/GitHub/SimToolChain/Merge/Kuhburg/WholeField/'
  file4: 020-1_KUHBURG_WW-1Z0S685AKFM094700_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file5: 020-1_KUHBURG_WW-1Z0S685AAFM094704_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file6: 020-1_KUHBURG_WW-1Z0S685AVFM094684_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file7: //iso19prod/IntelligentCombine/HA/ISE/reports/data/sfcVarMapping.csv
  tz: "Canada/Central"
---

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(comment=NA, echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dbplyr)
library(tinytex)
library(colorRamps)
library(knitr)
library(kableExtra)
library(gridExtra)
library(grid)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(scales)
library(data.table)

source("src/versatility.R")
source("src/plotUtil.R")
source("src/tableUtil.R")

```


```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE, }
##########Read in files##########
setwd(params$path)
asHarvest        <- read.csv(params$file1, header = TRUE, as.is = TRUE)
asHarvest        <- rbind(asHarvest, read.csv(params$file2, header = TRUE, as.is = TRUE))
asHarvest        <- rbind(asHarvest, read.csv(params$file3, header = TRUE, as.is = TRUE))
simulatedHarvest <- read.csv(params$file4, header = FALSE, as.is = TRUE)
simulatedHarvest <- rbind(simulatedHarvest, read.csv(params$file5, header = FALSE, as.is = TRUE))
simulatedHarvest <- rbind(simulatedHarvest, read.csv(params$file6, header = FALSE, as.is = TRUE))
headerNames      <- read.csv(params$file7, header = TRUE)

##########Put Header names in##########
# names(asHarvest)        <- headerNames$AWS
names(simulatedHarvest) <- headerNames$AWS


asHarvest        <- mutate(asHarvest, Source = "As Harvested")
simulatedHarvest <- mutate(simulatedHarvest, Source = "Simulated")
asHarvest[["time"]] <- NULL
asHarvest[["Index"]] <- NULL

# tidy the data before merging

asHarvest$hwu <- with(asHarvest, ifelse(is.na(hwu), hwi, hwu))


bindedDF  <- rbind(asHarvest, simulatedHarvest)
```

# Case Report for machine `r unique(bindedDF$serialnumber)`

```{r}
#######################################
#########Preparing Calculations########
#######################################

model <- bindedDF$serialnumber %>% unique(.) %>% substr(., 4, 7) %>% unique(.)

maxPower <- case_when(
  model == "S660" ~ 249,
  model == "S670" ~ 292,
  model == "S680" ~ 353,
  model == "S685" ~ 373,
  model == "S690" ~ 405,
  TRUE ~ as.numeric(NA)
)

bindedDF <- bindedDF %>%
  mutate(., pu = ep/373 * 100)
```


```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
#Harvest Performance Scores (AKA HPS)
#  overall performance, grain productivity, power utalization, fuel Economy, grain
#  saving

hpsTable <-
  createHPS(bindedDF)

#Harvesting Performance - Engineering Units (AKA HPEU)
# Grain Prod, Power Util, Fuel Econ, Total Loss

hpeuTable <-
  createHPEU(bindedDF)

#Power Summary (AKA PS)
# Engine Harv, Eng Harv and UL, Avg Harv Specific Pwr, Propulsion Power
psTable <-
  createPS(bindedDF)

engineHarvesting <- bindedDF %>%
  dplyr::filter(ms == 5) %>%
  dplyr::group_by(serialnumber, Source) %>%
  dplyr::summarise(EngineHarv = mean(ep, na.rm = TRUE))

psTable$EngineHarv <- engineHarvesting$EngineHarv

# agronomic and output summary (AKA AOS)
# Avg Harvest Speed, Harv Area, Avg Yield
aosTable <-
  createAOS(bindedDF)

# Rename col names

names(hpsTable) <- c("Machine",  "Overall Performance", "Grain Productivity", "Power Utilization", "Fuel Economy", "Grain Saving")

names(hpeuTable) <- c("Machine", "Grain Prod (t/h)", "Power Utl (%)", "Fuel Econ (1/t)")

names(psTable) <- c("Machine", "Engine Harv (kW)", "Eng Harv & Utl (kW)", "Avg Harv Specific Pwr (kW/t/h)", "Propulsion Power (kW)")

names(aosTable) <- c("Machine", "Avg Harvest Speed (km/h)", "Harv Area (ha)", "Avg Yield (t/ha)")

```

# Overall Performance Summary

## Field Harvesting Performance Summary

### Harvesting Performance Scores

```{r, results = "asis"}
machines <- unique(bindedDF$serialnumber)

output <- kable(hpsTable, digits = 0,"latex", booktabs = TRUE)

rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Harvesting Performance - Engineering Units

```{r, results = "asis"}
output <- kable(hpeuTable, digits = 1,"latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Power Summary

```{r, results = "asis"}
output <- kable(psTable, digits = 0, "latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Agronomic & Output Summary

```{r, results = "asis"}
output<- kable(aosTable, digits = 1, "latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

```{r}
bindedDF <- bindedDF %>% dplyr::filter(., ms == 4 | ms == 5)
```

```{r}
minX <- with(bindedDF, min(lon, na.rm = TRUE))
maxX <- with(bindedDF, max(lon, na.rm = TRUE))
minY <- with(bindedDF, min(lat, na.rm = TRUE))
maxY <- with(bindedDF, max(lat, na.rm = TRUE))

minX <- round(minX, 4) - 0.0001
maxX <- round(maxX, 4) + 0.0001
minY <- round(minY, 4) - 0.0001
maxY <- round(maxY, 4) + 0.0001

```


```{r}
# Calculate Zoom
bindedDFZoom <- calc_zoom(lon, lat, bindedDF) - 1

# Calculate Center of path
bindedDFlon <- (max(bindedDF$lon) + min(bindedDF$lon))/2
bindedDFlat <- (max(bindedDF$lat) + min(bindedDF$lat))/2

# Get The Maps
map <-
  get_map(location = c(lon = bindedDFlon, lat = bindedDFlat),
          zoom = bindedDFZoom, maptype = "satellite")

bindedDFscale <-
  data.frame(lat = c(min(bindedDF$lat), max(bindedDF$lat)),
             lon = c(min(bindedDF$lon), max(bindedDF$lon)))
```

```{r}
# Prepare separate dfs for plots
simDF <- bindedDF %>% dplyr::filter(Source == "Simulated")
harvDF <- bindedDF %>% dplyr::filter(Source == "As Harvested")



```

## As Harvested Ground Speed (GPSSP)

```{r}

# minZ   <- with(bindedDF, quantile(gpssp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(gpssp, params$pc, na.rm = TRUE))
# 
# bindedDF$gpssp2 <- with(bindedDF, ifelse(gpssp < minZ, minZ, gpssp))
# bindedDF$gpssp2 <- with(bindedDF, ifelse(gpssp2 > maxZ, maxZ, gpssp2))

mapDF <- limitVar(harvDF, "gpssp", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

densLim <- densLimit(harvDF, "gpssp", params$dpc)

plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = gpssp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Ground Speed, kph") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```

## Simulated Ground Speed (GPSSP)

```{r}
mapDF <- limitVar(simDF, "gpssp", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

densLim <- densLimit(simDF, "gpssp", params$dpc)

plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = gpssp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Ground Speed, kph") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```


## As Harvested Grain Productivity (PRO)

```{r}
# minZ   <- with(bindedDF, quantile(pro, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pro, params$pc, na.rm = TRUE))
# 
# bindedDF$pro2 <- with(bindedDF, ifelse(pro < minZ, minZ, pro))
# bindedDF$pro2 <- with(bindedDF, ifelse(pro2 > maxZ, maxZ, pro2))

mapDF <- limitVar(harvDF, "pro", params$pc)
densLim <- densLimit(harvDF, "pro", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()



plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = pro, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Grain Productivity, t/h") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```

## Simulated Grain Productivity (PRO)

```{r}
# minZ   <- with(bindedDF, quantile(pro, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pro, params$pc, na.rm = TRUE))
# 
# bindedDF$pro2 <- with(bindedDF, ifelse(pro < minZ, minZ, pro))
# bindedDF$pro2 <- with(bindedDF, ifelse(pro2 > maxZ, maxZ, pro2))

mapDF <- limitVar(simDF, "pro", params$pc)
densLim <- densLimit(simDF, "pro", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()



plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = pro, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Grain Productivity, t/h") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```

## As Harvested Power Utilization (100 * EP/MaxPower)

```{r}

# minZ   <- with(bindedDF, quantile(pu, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pu, params$pc, na.rm = TRUE))
# 
# bindedDF$pu2 <- with(bindedDF, ifelse(pu < minZ, minZ, pu))
# bindedDF$pu2 <- with(bindedDF, ifelse(pu2 > maxZ, maxZ, pu2))

mapDF <- limitVar(harvDF, "pu", params$pc)
densLim <- densLimit(harvDF, "pu", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = pu, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs( x = "Power Utilization, %") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")


grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```

## Simulated Power Utilization (100 * EP/MaxPower)

```{r}

# minZ   <- with(bindedDF, quantile(pu, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pu, params$pc, na.rm = TRUE))
# 
# bindedDF$pu2 <- with(bindedDF, ifelse(pu < minZ, minZ, pu))
# bindedDF$pu2 <- with(bindedDF, ifelse(pu2 > maxZ, maxZ, pu2))

mapDF <- limitVar(simDF, "pu", params$pc)
densLim <- densLimit(simDF, "pu", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = pu, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs( x = "Power Utilization, %") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")


grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```

## As Harvested Fuel Consumption

```{r}

# asfcihFrame <- dplyr::filter(asHarvest, fcih <= 10)
# simfcihFrame <- dplyr::filter(simulatedHarvest, fcih <= 10)
# 
# minZ   <-  bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, 1 - params$pc, na.rm = TRUE))
# maxZ   <- bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, params$pc, na.rm = TRUE))

mapDF <- limitVar(harvDF, "fcih", params$pc)
densLim <- densLimit(harvDF, "fcih", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = fcih, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Fuel Consumption, l/t") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```

## Simulated Fuel Consumption

```{r}

# asfcihFrame <- dplyr::filter(asHarvest, fcih <= 10)
# simfcihFrame <- dplyr::filter(simulatedHarvest, fcih <= 10)
# 
# minZ   <-  bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, 1 - params$pc, na.rm = TRUE))
# maxZ   <- bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, params$pc, na.rm = TRUE))

mapDF <- limitVar(simDF, "fcih", params$pc)
densLim <- densLimit(simDF, "fcih", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = fcih, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Fuel Consumption, l/t") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))

```

## As Harvest Rotor Drive Pressure (RDP)

```{r}

# minZ   <- with(bindedDF, quantile(rdp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(rdp, params$pc, na.rm = TRUE))
# 
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp < minZ, minZ, rdp))
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp2 > maxZ, maxZ, rdp2))

mapDF <- limitVar(harvDF, "rdp", params$pc)
densLim <- densLimit(harvDF, "rdp", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = rdp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Rotor Drive Pressure, mV") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```


## Simulated Rotor Drive Pressure (RDP)

```{r}

# minZ   <- with(bindedDF, quantile(rdp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(rdp, params$pc, na.rm = TRUE))
# 
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp < minZ, minZ, rdp))
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp2 > maxZ, maxZ, rdp2))

mapDF <- limitVar(simDF, "rdp", params$pc)
densLim <- densLimit(simDF, "rdp", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = rdp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Rotor Drive Pressure, mV") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```




## As Harvested Propulsion Power (PP)

```{r}
# minZ   <- with(bindedDF, quantile(pp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pp, params$pc, na.rm = TRUE))
# 
# bindedDF$pp2 <- with(bindedDF, ifelse(pp < minZ, minZ, pp))
# bindedDF$pp2 <- with(bindedDF, ifelse(pp2 > maxZ, maxZ, pp2))

mapDF <- limitVar(harvDF, "pp", params$pc)
densLim <- densLimit(harvDF, "pp", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = harvDF) +
  geom_density(aes(x = pp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Propulsion Power, kW") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```

## Simulated Propulsion Power (PP)

```{r}
# minZ   <- with(bindedDF, quantile(pp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pp, params$pc, na.rm = TRUE))
# 
# bindedDF$pp2 <- with(bindedDF, ifelse(pp < minZ, minZ, pp))
# bindedDF$pp2 <- with(bindedDF, ifelse(pp2 > maxZ, maxZ, pp2))

mapDF <- limitVar(simDF, "pp", params$pc)
densLim <- densLimit(simDF, "pp", params$dpc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  mapTheme()

rightPlot <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~serialnumber, ncol = 1) +
  rightTheme()

plotDensity <- ggplot(data = simDF) +
  geom_density(aes(x = pp, color = serialnumber), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Propulsion Power, kW") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             rightPlot,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(1,1,1,2,2,2),
                                   c(3,3,3,2,2,2),
                                   c(3,3,3,2,2,2)))
```


