---
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_width: 25
    fig_height: 25
classoption: landscape
geometry: margin=2cm
params:
  pc: 0.8
  dpc: 0.98
  file1: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AAFM094704-HA.csv
  path: '~/GitHub/SimToolChain/Merge/Kuhburg/'
  file2: 020-1_KUHBURG_WW-1Z0S685AAFM094704_MPC_EP100_PerfectPredictions_min-sim_processed.csv
  file3: //iso19prod/IntelligentCombine/HA/ISE/reports/data/sfcVarMapping.csv
  tz: "Europe/Berlin"
---

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(comment=NA, echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dbplyr)
library(tinytex)
library(colorRamps)
library(knitr)
library(kableExtra)
library(gridExtra)
library(grid)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(scales)
library(data.table)
library(pander)

source("src/versatility.R")
source("src/plotUtil.R")
source("src/tableUtil.R")
```


```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE, }
setwd(params$path)
asHarvest        <- read.csv(params$file1, header = TRUE, as.is = TRUE)
simulatedHarvest <- read.csv(params$file2, header = FALSE, as.is = TRUE)
headerNames      <- read.csv(params$file3, header = TRUE)

names(simulatedHarvest) <- headerNames$AWS

asHarvest        <- mutate(asHarvest, Source = "As Harvested")
simulatedHarvest <- mutate(simulatedHarvest, Source = "Simulated")
asHarvest[["time"]] <- NULL
asHarvest[["Index"]] <- NULL

asHarvest$hwu <- with(asHarvest, ifelse(is.na(hwu), hwi, hwu))

bindedDF  <- rbind(asHarvest, simulatedHarvest)
```

# Case Report for machine `r unique(bindedDF$serialnumber)`

```{r}
model <- bindedDF$serialnumber %>% unique(.) %>% substr(., 4, 7) %>% unique(.)

maxPower <- case_when(
  model == "S660" ~ 249,
  model == "S670" ~ 292,
  model == "S680" ~ 353,
  model == "S685" ~ 373,
  model == "S690" ~ 405,
  TRUE ~ as.numeric(NA)
)

bindedDF <- bindedDF %>%
  mutate(., pu = ep/maxPower * 100)
```

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
#Harvest Performance Scores (AKA HPS)
#  overall performance, grain productivity, power utalization, fuel Economy, grain
#  saving

hpsTable <-
  createHPS(bindedDF)

#Harvesting Performance - Engineering Units (AKA HPEU)
# Grain Prod, Power Util, Fuel Econ, Total Loss

hpeuTable <-
  createHPEU(bindedDF)

#Power Summary (AKA PS)
# Engine Harv, Eng Harv and UL, Avg Harv Specific Pwr, Propulsion Power
# !NOTE!: engineHarvesting Metric only looks at machine state 5! 
psTable <-
  createPS(bindedDF)

engineHarvesting <- bindedDF %>%
  dplyr::filter(ms == 5) %>%
  dplyr::group_by(serialnumber, Source) %>%
  dplyr::summarise(EngineHarv = mean(ep, na.rm = TRUE))

psTable$EngineHarv <- engineHarvesting$EngineHarv

# agronomic and output summary (AKA AOS)
# Avg Harvest Speed, Harv Area, Avg Yield
aosTable <-
  createAOS(bindedDF)
```

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
# Rename the column names for better output readability

names(hpsTable) <- c("Machine",  "Overall Performance", "Grain Productivity", "Power Utilization", "Fuel Economy", "Grain Saving")

names(hpeuTable) <- c("Machine", "Grain Prod (t/h)", "Power Utl (%)", "Fuel Econ (1/t)")

names(psTable) <- c("Machine", "Engine Harv (kW)", "Eng Harv & Utl (kW)", "Avg Harv Specific Pwr (kW/t/h)", "Propulsion Power (kW)")

names(aosTable) <- c("Machine", "Avg Harvest Speed (km/h)", "Harv Area (ha)", "Avg Yield (t/ha)")

```

# Overall Performance Summary

## Field Harvesting Performance Summary

### Harvesting Performance Scores

```{r, results = "asis"}
machines <- unique(bindedDF$serialnumber)

output <- kable(hpsTable, digits = 0,"latex", booktabs = TRUE)

rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Harvesting Performance - Engineering Units

```{r, results = "asis"}
output <- kable(hpeuTable, digits = 1,"latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Power Summary

```{r, results = "asis"}
output <- kable(psTable, digits = 0, "latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

### Agronomic & Output Summary

```{r, results = "asis"}
output<- kable(aosTable, digits = 1, "latex", booktabs = TRUE)
rnum <- 1
for(i in seq_along(machines)){
  output <- output %>% 
    group_rows(machines[i], rnum, rnum + 1)
  rnum <- rnum + 2
}

output
```

```{r}
bindedDF <- bindedDF %>% dplyr::filter(., ms == 4 | ms == 5)
```

```{r}
minX <- with(bindedDF, min(lon, na.rm = TRUE))
maxX <- with(bindedDF, max(lon, na.rm = TRUE))
minY <- with(bindedDF, min(lat, na.rm = TRUE))
maxY <- with(bindedDF, max(lat, na.rm = TRUE))

minX <- round(minX, 4) - 0.0001
maxX <- round(maxX, 4) + 0.0001
minY <- round(minY, 4) - 0.0001
maxY <- round(maxY, 4) + 0.0001

```



```{r}
# Calculate Zoom
bindedDFZoom <- calc_zoom(lon, lat, bindedDF) - 1

# Calculate Center of path
bindedDFlon <- (max(bindedDF$lon) + min(bindedDF$lon))/2
bindedDFlat <- (max(bindedDF$lat) + min(bindedDF$lat))/2

# Get The Maps
map <-
  get_map(location = c(lon = bindedDFlon, lat = bindedDFlat),
          zoom = bindedDFZoom, maptype = "satellite")

bindedDFscale <-
  data.frame(lat = c(min(bindedDF$lat), max(bindedDF$lat)),
             lon = c(min(bindedDF$lon), max(bindedDF$lon)))


```

## Harvesting Ground Speed (GPSSP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "gpssp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "gpssp", 
  pc = params$dpc, 
  label = "Ground Speed, kph")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Grain Productivity (PRO)

```{r}
plotAsHarvest <- plotMap(map, bindedDF, "pro", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pro", 
  pc = params$dpc, 
  label = "Grain Productivity, t/h")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Power Utilization (100 * EP/MaxPower)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "pu", params$pc)

densLim <- densLimit(bindedDF, "pu", params$dpc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pu", 
  pc = params$dpc, 
  label = "Power Utilization, %")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Consumption

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "fcih", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "fcih", 
  pc = params$dpc, 
  label = "Fuel Consumption, l/t")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Rotor Drive Pressure (RDP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "rdp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "rdp", 
  pc = params$dpc, 
  label = "Rotor Drive Pressure, mV")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Propulsion Power (PP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "pp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pp", 
  pc = params$dpc, 
  label = "Propulsion Power, kW")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Consumption vs Grain Productivity

```{r}
yLim <- densLimit(bindedDF, "fcih", params$dpc)
xLim <- densLimit(bindedDF, "pro", params$dpc)

ggplot(data = bindedDF, aes(x = pro, y = fcih, color = Source), size = 2) +
  scale_x_continuous(limits = c(xLim$minZ[1], xLim$maxZ[1]), expand = c(0, 0)) +
  scale_y_continuous(limits = c(yLim$minZ[1], yLim$maxZ[1]), expand = c(0, 0)) +
  geom_point( alpha=0.35) +
  stat_density_2d(size = 1, contour = TRUE) +
  onePlot() +
  labs(x = "Grain Productivity, t/h", y = "Fuel Consumption, l/t")
```

## Overall Performance (OPSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "opscore", 
                         pc = params$pc, 
                         score = TRUE)
  
plotDensity <- plotDens(df = bindedDF, 
                        item = "opscore",
                        pc = params$dpc,
                        label = "Overall Performance Score",
                        score = TRUE) 


grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Grain Productivity (GPSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "gpscore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "gpscore",
                        pc = params$dpc,
                        label = "Grain Productivity Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Power Utilization Score (PUSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "puscore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "puscore",
                        pc = params$dpc,
                        label = "Power Utilization Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Economy Score (FESCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "fescore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "fescore",
                        pc = params$dpc,
                        label = "Fuel Economy Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

```{r}
# Convert GPS time to field time to prepare for Versatility Calculations

df <- asHarvest
df$Source <- "As Harvested"
df$DateTime <- with(df,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

asHarvFilt <- df %>% dplyr::filter(., ms == 4 | ms == 5)

df2 <- simulatedHarvest
df2$Source <- "Simulated"
df2$DateTime <- with(df2,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simHarvFilt <- df2  %>% dplyr::filter(., ms == 4 | ms == 5)

df <- rbind(df, df2)
df <- df %>% dplyr::filter(., ms == 4 | ms == 5)
df$dateCode <-  strftime(df$DateTime, format = "%Y-%m-%d" )




```

```{r}

startTime <- strptime("00:00:00", format = "%H:%M:%S")

simHarvFilt$epoc <- startTime + as.numeric(row.names(simHarvFilt)) - 1
asHarvFilt$epoc <- startTime + as.numeric(row.names(asHarvFilt)) - 1

epocDF <- rbind(simHarvFilt, asHarvFilt)
epocDF$dateCode <-  strftime(epocDF$DateTime, format = "%Y-%m-%d" )
asHarvFilt <- asHarvFilt[1:dim(simHarvFilt)[1], ]
filtDF <- rbind(asHarvFilt, simHarvFilt)
filtDF$dateCode <-  strftime(filtDF$DateTime, format = "%Y-%m-%d" )

```

```{r title, results='asis', fig.width=8, fig.height=3}
# The following are versatility table output and time vs metric plotting
# The for-loops are used to create versatility pages for each unique date

for( i in unique(df$dateCode)){
  cat("\\pagebreak")
  
  VersDF <- epocDF %>% 
    dplyr::filter(., dateCode == i)
  VersDF$time <- VersDF$DateTime
  VersDF$model_year <- substr(VersDF$serialnumber, 10, 10)
  VersDF$model <- VersDF$serialnumber %>% substr(., 4, 7)
  VersDF$machine_name <- VersDF$Source
  
  paramFiltDF <- filtDF %>% 
    dplyr::filter(., dateCode == i)
  paramFiltDF$time <- paramFiltDF$DateTime
  paramFiltDF$model_year <- substr(paramFiltDF$serialnumber, 10, 10)
  paramFiltDF$model <- paramFiltDF$serialnumber %>% substr(., 4, 7)
  paramFiltDF$machine_name <- paramFiltDF$Source
  
  p1 <- ggplot(VersDF, aes(x = epoc, y = pro, colour = Source)) +
    geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
    coord_cartesian(ylim=c(0, 100) + c(0,1)) +
    timeTheme() +
    labs(x = "Time", y = "Grain Productivity, t/h")
  
  pandoc.header(paste("Grain Productivity", i, sep = " "), level=2)
  
  vtab <- get_versatility_tbl(unique(bindedDF$field)[1], "pro", VersDF)
  appendParams <- newParamTable(unique(bindedDF$field)[1], "pro", paramFiltDF)
  
  print(p1)
  cat(vtab[1], "\n")
  cat(vtab[2], "\n")
  cat(appendParams, "\n")
  
  
}

for( i in unique(df$dateCode)){
  cat("\\pagebreak")
  
  VersDF <- epocDF %>% 
    dplyr::filter(., dateCode == i)
  VersDF$time <- VersDF$DateTime
  VersDF$model_year <- substr(VersDF$serialnumber, 10, 10)
  VersDF$model <- VersDF$serialnumber %>% substr(., 4, 7)
  VersDF$machine_name <- VersDF$Source
  
  paramFiltDF <- filtDF %>% 
    dplyr::filter(., dateCode == i)
  paramFiltDF$time <- paramFiltDF$DateTime
  paramFiltDF$model_year <- substr(paramFiltDF$serialnumber, 10, 10)
  paramFiltDF$model <- paramFiltDF$serialnumber %>% substr(., 4, 7)
  paramFiltDF$machine_name <- paramFiltDF$Source
  
  p1 <- ggplot(VersDF, aes(x = epoc, y = gpscore, colour = Source)) +
    geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
    coord_cartesian(ylim=c(0, 100) + c(0,1)) +
    timeTheme() +
    labs(x = "Time", y = "Grain Productivity Score")
  pandoc.header(paste("Grain Productivity Score", i, sep = " "), level=2)
  vtab <- get_versatility_tbl(unique(bindedDF$field)[1], "gpscore", VersDF)
  appendParams <- newParamTable(unique(bindedDF$field)[1], "gpscore", paramFiltDF)
  
  print(p1)
  cat(vtab[1], "\n")
  cat(vtab[2], "\n")
  cat(appendParams, "\n")
  
  
}
```

## Speed vs. Propulsion Power

```{r}
xLim <- densLimit(bindedDF, "gpssp", params$dpc)
yLim <- densLimit(bindedDF, "pp", params$dpc)

ggplot(bindedDF, aes(x = gpssp, y = pp, colour = Source)) +
  geom_point(alpha = 0.25, size = 0.5) +
  scale_x_continuous(limits = c(xLim$minZ[1], xLim$maxZ[1])) +
  scale_y_continuous(limits = c(yLim$minZ[1], yLim$maxZ[1])) +
  geom_smooth(method = lm, se = FALSE) +
  onePlot() +
  labs(x = "Speed, kph", y = "Propulsion Power, kW")
```
