---
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_width: 25
    fig_height: 25
classoption: landscape
geometry: margin=2cm
params:
  pc: 0.8
  dpc: 0.98
  file1: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AVFM094684-HA.csv
  path: '~/GitHub/SimToolChain/Merge/MergeOutput'
  file2: 020-1_KUHBURG_WW-1Z0S685AVFM094684_MPC_EP100_PerfectPredictions_min-sim_processed.csv
  file3: //iso19prod/IntelligentCombine/HA/ISE/reports/data/sfcVarMapping.csv
  tz: "Germany/Berlin"
---

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(comment=NA, echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dbplyr)
library(tinytex)
library(colorRamps)
library(knitr)
library(gridExtra)
library(grid)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(scales)
library(data.table)

source("src/versatility.R")
source("src/plotUtil.R")

```


```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE, }
##########Read in files##########
setwd(params$path)
asHarvest        <- read.csv(params$file1, header = TRUE, as.is = TRUE)
simulatedHarvest <- read.csv(params$file2, header = FALSE, as.is = TRUE)
headerNames      <- read.csv(params$file3, header = TRUE)

##########Put Header names in##########
# names(asHarvest)        <- headerNames$AWS
names(simulatedHarvest) <- headerNames$AWS


asHarvest        <- mutate(asHarvest, Source = "As Harvested")
simulatedHarvest <- mutate(simulatedHarvest, Source = "Simulated")
asHarvest[["time"]] <- NULL
asHarvest[["Index"]] <- NULL

# tidy the data before merging

asHarvest$hwu <- with(asHarvest, ifelse(is.na(hwu), hwi, hwu))


bindedDF  <- rbind(asHarvest, simulatedHarvest)
```

# Case Report for machine `r unique(bindedDF$serialnumber)`

```{r}
#######################################
#########Preparing Calculations########
#######################################

model <- bindedDF$serialnumber %>% unique(.) %>% substr(., 4, 7)

maxPower <- case_when(
  model == "S660" ~ 249,
  model == "S670" ~ 292,
  model == "S680" ~ 353,
  model == "S685" ~ 373,
  model == "S690" ~ 405,
  TRUE ~ as.numeric(NA)
)

bindedDF <- bindedDF %>%
  mutate(., pu = ep/maxPower * 100)
```

```{r}
#######################################
#########Preparing the Tables##########
#######################################
```
```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
#Harvest Performance Scores (AKA HPS)
#  overall performance, grain productivity, power utalization, fuel Economy, grain
#  saving

hpsTable <-
  bindedDF %>% dplyr::filter(ms == 4 | ms == 5) %>% dplyr::group_by(Source) %>% dplyr::summarise(
    Performance = mean(opscore, na.rm = TRUE),
    Productivity = mean(gpscore, na.rm = TRUE),
    Power = mean(puscore, na.rm = TRUE),
    Fuel = mean(fescore, na.rm = TRUE),
    Grain = mean(glscore, na.rm = TRUE)
  )

#Harvesting Performance - Engineering Units (AKA HPEU)
# Grain Prod, Power Util, Fuel Econ, Total Loss

hpeuTable <-
  bindedDF %>%
  dplyr::filter(ms == 4 | ms == 5) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(
    GrainProd = mean(pro, na.rm = TRUE),
    PowerUtil = mean(pu, na.rm = TRUE),
    FuelEcon = mean(fcih, na.rm = TRUE)
  )

#Power Summary (AKA PS)
# Engine Harv, Eng Harv and UL, Avg Harv Specific Pwr, Propulsion Power
psTable <-
  bindedDF %>%
  dplyr::filter(ms == 4 | ms == 5 ) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(
    EngineHarv = mean(ep, na.rm = TRUE),
    EngineHarvUL = mean(ep, na.rm = TRUE),
    AvgHarvSpecificPwr = mean(ifelse(pro == 0, NA, ep/pro), na.rm = TRUE),
    PropulsionPower = mean(pp, na.rm = TRUE)
  )

engineHarvesting <- bindedDF %>%
  dplyr::filter(ms == 5) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(EngineHarv = mean(ep, na.rm = TRUE))

psTable$EngineHarv <- engineHarvesting$EngineHarv

# agronomic and output summary (AKA AOS)
# Avg Harvest Speed, Harv Area, Avg Yield
aosTable <-
  bindedDF %>% 
  dplyr::filter(ms == 4 | ms == 5) %>% 
  dplyr::group_by(Source) %>% 
  dplyr::summarize(
    HarvestSpeed = mean(gpssp, na.rm = TRUE),
    HarvestArea = sum(gpssp * pmin(hwu, hwi, na.rm = TRUE) / 36000, na.rm = TRUE),
    AvgYield = mean(yield, na.rm = TRUE)
  )

############################################
#       Rename the tables                  #
#   Rename row names to source             #
#   Rename the col names to proper titles  #
############################################

row.names(hpsTable) <- hpsTable$Source
hpsTable$Source <- NULL
  names(hpsTable) <- c("Overall Performance", "Grain Productivity", "Power Utilization", "Fuel Economy", "Grain Saving")


row.names(hpeuTable) <- hpeuTable$Source
hpeuTable$Source <- NULL
names(hpeuTable) <- c("Grain Prod (t/h)", "Power Utl (%)", "Fuel Econ (1/t)")


row.names(psTable) <- psTable$Source
psTable$Source <- NULL
names(psTable) <- c("Engine Harv (kW)", "Eng Harv & Utl (kW)", "Avg Harv Specific Pwr (kW/t/h)", "Propulsion Power (kW)")


row.names(aosTable) <- aosTable$Source
aosTable$Source <- NULL
names(aosTable) <- c("Avg Harvest Speed (km/h)", "Harv Area (ha)", "Avg Yield (t/ha)")

```

# Overall Performance Summary

## Field Harvesting Performance Summary

### Harvesting Performance Scores

```{r, results = "asis"}
kable(round(hpsTable, digits = 0), "latex", booktabs = TRUE)
```

### Harvesting Performance - Engineering Units

```{r, results = "asis"}

kable(round(hpeuTable, digits = 1),"latex", booktabs = TRUE)
```

### Power Summary

```{r, results = "asis"}
kable(round(psTable, digits = 0), "latex", booktabs = TRUE)
```

### Agronomic & Output Summary

```{r, results = "asis"}
kable(round(aosTable, digits = 1), "latex", booktabs = TRUE)
```

```{r}
bindedDF <- bindedDF %>% dplyr::filter(., ms == 4 | ms == 5)
```

```{r}
minX <- with(bindedDF, min(lon, na.rm = TRUE))
maxX <- with(bindedDF, max(lon, na.rm = TRUE))
minY <- with(bindedDF, min(lat, na.rm = TRUE))
maxY <- with(bindedDF, max(lat, na.rm = TRUE))

minX <- round(minX, 4) - 0.0001
maxX <- round(maxX, 4) + 0.0001
minY <- round(minY, 4) - 0.0001
maxY <- round(maxY, 4) + 0.0001

```



```{r}
# Calculate Zoom
bindedDFZoom <- calc_zoom(lon, lat, bindedDF) - 1

# Calculate Center of path
bindedDFlon <- (max(bindedDF$lon) + min(bindedDF$lon))/2
bindedDFlat <- (max(bindedDF$lat) + min(bindedDF$lat))/2

# Get The Maps
map <-
  get_map(location = c(lon = bindedDFlon, lat = bindedDFlat),
          zoom = bindedDFZoom, maptype = "satellite")

bindedDFscale <-
  data.frame(lat = c(min(bindedDF$lat), max(bindedDF$lat)),
             lon = c(min(bindedDF$lon), max(bindedDF$lon)))


```

## Harvesting Ground Speed (GPSSP)

```{r}

# minZ   <- with(bindedDF, quantile(gpssp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(gpssp, params$pc, na.rm = TRUE))
# 
# bindedDF$gpssp2 <- with(bindedDF, ifelse(gpssp < minZ, minZ, gpssp))
# bindedDF$gpssp2 <- with(bindedDF, ifelse(gpssp2 > maxZ, maxZ, gpssp2))

mapDF <- limitVar(bindedDF, "gpssp", params$pc)


plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


densLim <- densLimit(bindedDF, "gpssp", params$dpc)

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = gpssp, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Ground Speed, kph") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))

```

## Grain Productivity (PRO)

```{r}
# minZ   <- with(bindedDF, quantile(pro, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pro, params$pc, na.rm = TRUE))
# 
# bindedDF$pro2 <- with(bindedDF, ifelse(pro < minZ, minZ, pro))
# bindedDF$pro2 <- with(bindedDF, ifelse(pro2 > maxZ, maxZ, pro2))

mapDF <- limitVar(bindedDF, "pro", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()

densLim <- densLimit(bindedDF, "pro", params$dpc)

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = pro, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs( x = "Grain Productivity, t/h") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))

```

## Power Utilization (100 * EP/MaxPower)

```{r}

# minZ   <- with(bindedDF, quantile(pu, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pu, params$pc, na.rm = TRUE))
# 
# bindedDF$pu2 <- with(bindedDF, ifelse(pu < minZ, minZ, pu))
# bindedDF$pu2 <- with(bindedDF, ifelse(pu2 > maxZ, maxZ, pu2))

mapDF <- limitVar(bindedDF, "pu", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()

densLim <- densLimit(bindedDF, "pu", params$dpc)

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = pu, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs( x = "Power Utilization, %") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")


grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Fuel Consumption

```{r}

# asfcihFrame <- dplyr::filter(asHarvest, fcih <= 10)
# simfcihFrame <- dplyr::filter(simulatedHarvest, fcih <= 10)
# 
# minZ   <-  bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, 1 - params$pc, na.rm = TRUE))
# maxZ   <- bindedDF %>%
#   dplyr::filter(fcih <= 10) %>%
#   with( quantile(fcih, params$pc, na.rm = TRUE))

mapDF <- limitVar(bindedDF, "fcih", params$pc)


plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


densLim <- densLimit(bindedDF, "fcih", params$dpc)

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = fcih, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Fuel Consumption, l/t") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))

```

## Rotor Drive Pressure (RDP)

```{r}

# minZ   <- with(bindedDF, quantile(rdp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(rdp, params$pc, na.rm = TRUE))
# 
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp < minZ, minZ, rdp))
# bindedDF$rdp2 <- with(bindedDF, ifelse(rdp2 > maxZ, maxZ, rdp2))

mapDF <- limitVar(bindedDF, "rdp", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()

densLim <- densLimit(bindedDF, "rdp", params$dpc)

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = rdp, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Rotor Drive Pressure, mV") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Propulsion Power (PP)

```{r}
# minZ   <- with(bindedDF, quantile(pp, 1 - params$pc, na.rm = TRUE))
# maxZ   <- with(bindedDF, quantile(pp, params$pc, na.rm = TRUE))
# 
# bindedDF$pp2 <- with(bindedDF, ifelse(pp < minZ, minZ, pp))
# bindedDF$pp2 <- with(bindedDF, ifelse(pp2 > maxZ, maxZ, pp2))

mapDF <- limitVar(bindedDF, "pp", params$pc)

plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1]-1, mapDF$maxZ[1]+1),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()

densLim <- densLimit(bindedDF, "pp", params$dpc)

pplotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = pp, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Propulsion Power, kW") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Fuel Consumption vs Grain Productivity

```{r}
yLim <- densLimit(bindedDF, "fcih", params$dpc)
xLim <- densLimit(bindedDF, "pro", params$dpc)
ggplot(data = bindedDF, aes(x = pro, y = fcih, color = Source), size = 2) +
  scale_x_continuous(limits = xLim, expand = c(0, 0)) +
  scale_y_continuous(limits = yLim, expand = c(0, 0)) +
  geom_point( alpha=0.35) +
  stat_density_2d(size = 1, contour = TRUE) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 25),
    axis.title = element_text(size = 30),
    axis.text = element_text(size = 20),
    panel.background =  element_rect(fill = "white", colour = NA), 
    panel.border =      element_rect(fill = NA, colour="grey50"), 
    panel.grid.major =  element_line(colour = "grey90", size = 0.2),
    panel.grid.minor =  element_line(colour = "grey98", size = 0.5),
    panel.margin =      unit(0.25, "lines") 
  ) +
  labs(x = "Grain Productivity, t/h", y = "Fuel Consumption, l/t")
```

## Overall Performance (OPSCORE)

```{r}
minZ   <- 0
maxZ   <- 100

plotAsHarvest <-
  ggmap(map) +
  geom_point(data = bindedDF,aes(x = lon, y = lat, colour = opscore)) +
  scale_colour_gradientn(limits = c(minZ, maxZ),
                         colours = matlab.like(64),
                         guide = guide_colorbar(barwidth = unit(.45, "npc"))) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


plotDensity <- ggplot(data = bindedDF) +
  geom_density( aes(x = opscore, color = Source), size = 2) +
  densTheme() +
  labs(x = "Overall Performance Score") +
  scale_x_continuous(limits = c(minZ, maxZ) ) +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Grain Productivity (GPSCORE)
```{r}


plotAsHarvest <-
  ggmap(map) +
  geom_point(data = bindedDF,aes(x = lon, y = lat, colour = gpscore)) +
  scale_colour_gradientn(limits = c(minZ, maxZ),
                         colours = matlab.like(64),
                         guide = guide_colorbar(barwidth = unit(.45, "npc"))) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = gpscore, color = Source), size = 2) +
  densTheme() +
  labs(x = "Grain Productivity Score") +
  scale_x_continuous(limits = c(minZ, maxZ) ) +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Power Utilization Score (PUSCORE)

```{r}

plotAsHarvest <-
  ggmap(map) +
  geom_point(data = bindedDF,aes(x = lon, y = lat, colour = puscore)) +
  scale_colour_gradientn(limits = c(minZ, maxZ),
                         colours = matlab.like(64),
                         guide = guide_colorbar(barwidth = unit(.45, "npc"))) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


plotDensity <- ggplot(data = bindedDF) +
  geom_density( aes(x = puscore, color = Source), size = 2) +
  densTheme() +
  labs(x = "Power Utilization Score") +
  scale_x_continuous(limits = c(minZ, maxZ) ) +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

## Fuel Economy Score (FESCORE)

```{r}

plotAsHarvest <-
  ggmap(map) +
  geom_point(data = bindedDF,aes(x = lon, y = lat, colour = fescore)) +
  scale_colour_gradientn(limits = c(minZ, maxZ),
                         colours = matlab.like(64),
                         guide = guide_colorbar(barwidth = unit(.45, "npc"))) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()

plotDensity <- ggplot(data = bindedDF) +
  geom_density(aes(x = fescore, color = Source), size = 2) +
  densTheme() +
  labs(x = "Fuel Economy Score") +
  scale_x_continuous(limits = c(minZ, maxZ) ) +
  geom_hline(yintercept = 0, size = 2, colour = "gray")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))
```

```{r}
df <- asHarvest
df$Source <- "As Harvested"
df$DateTime <- with(df,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

df2 <- simulatedHarvest
df2$Source <- "Simulated"
df2$DateTime <- with(df2,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)
# df2 <- simulatedHarvest
# df2$Source <- "Simulated"
# df2$DateTime <- df2$myjduserid

df <- rbind(df, df2)

df <- df %>% dplyr::filter(., ms == 4 | ms == 5)
```


```{r, fig.width=8, fig.height=3}
# Grain Productivity vs Time plot
ggplot(df, aes(x = DateTime, y = pro, colour = Source)) +
  geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
  coord_cartesian(ylim=c(0, 100) + c(0,1)) +
  timeTheme() +
  labs(x = "Time", y = "Grain Productivity, t/h")

```


```{r, results = 'asis'}
# Grain Productivity Versatility Table

VersDF <- df
colnames(VersDF)[which(names(VersDF) == "Source")] <- "machine_name"
VersDF$time <- VersDF$DateTime
VersDF$localtime <- VersDF$DateTime
VersDF$model_year <- substr(VersDF$serialnumber, 10, 10)
VersDF$model <- VersDF$serialnumber %>% substr(., 4, 7)

vtab <- get_versatility_tbl(unique(bindedDF$field)[1], "pro", VersDF)

cat(vtab[1], "\n")
cat(vtab[2], "\n")

```


```{r, fig.width=8, fig.height=3}
# Productivity Score vs Time plot
ggplot(df, aes(x = DateTime, y = gpscore, colour = Source)) +
  geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
  coord_cartesian(ylim=c(0, 100) + c(0,1)) +
  timeTheme() +
  labs(x = "Time", y = "Grain Productivity Score")
```


```{r, results = 'asis'}
VersDF <- df
colnames(VersDF)[which(names(VersDF) == "Source")] <- "machine_name"
VersDF$time <- VersDF$DateTime
VersDF$model_year <- substr(VersDF$serialnumber, 10, 10)
VersDF$model <- VersDF$serialnumber %>% substr(., 4, 7)

vtab <- get_versatility_tbl(unique(bindedDF$field)[1], "gpscore", VersDF)

cat(vtab[1], "\n")
cat(vtab[2], "\n")
```

## Speed vs. Propulsion Power

```{r}
xLim <- densLimit(bindedDF, "gpssp", params$dpc)
yLim <- densLimit(bindedDF, "pp", params$dpc)

ggplot(bindedDF, aes(x = gpssp, y = pp, colour = Source)) +
  geom_point(alpha = 0.25, size = 0.5) +
  scale_x_continuous(limits = xLim) +
  scale_y_continuous(limits = yLim) +
  geom_smooth(method = lm, se = FALSE) +
  onePlot() +
  labs(x = "Speed, kph", y = "Propulsion Power, kW")


```

## Log( Fuel Consumption ) vs. Log ( Productivity ) 

```{r}

# ggplot(data = bindedDF, aes(x = log(pro + 1), y = log(fcih + 1), color = Source)) +
#   geom_point()

bindedDF2 <- bindedDF %>% dplyr::filter(., fcih > 0)
bindedDF2 <- bindedDF2 %>% dplyr::filter(., pro > 0)

ggplot(data = bindedDF2, aes(x = log(pro), y = log(fcih), color = Source)) +
  geom_point(alpha = 0.25, size = 0.5) +
  geom_smooth(method = lm, se = FALSE) +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text = element_text(size = 25),
    axis.title = element_text(size = 30),
    axis.text = element_text(size = 20),
    panel.background =  element_rect(fill = "white", colour = NA), 
    panel.border =      element_rect(fill = NA, colour="grey50"), 
    panel.grid.major =  element_line(colour = "grey90", size = 0.2),
    panel.grid.minor =  element_line(colour = "grey98", size = 0.5),
    panel.margin =      unit(0.25, "lines") 
  ) 

```

## Fuel Consumption Error  vs. Productivity Error

```{r}
#summary(lm(log(fcih + 1) ~ log(pro + 1) + as.factor(Source), data = bindedDF))

#bindedDF$error <- resid(lm(log(fcih + 1) ~ log(pro + 1) + as.factor(Source), 
#                           data = bindedDF, na.action =  na.exclude))

#bindedDF2$error <- resid(lm(log(fcih + 1) ~ log(pro + 1), 
#                           data = bindedDF2, na.action =  na.exclude))

bindedDF2$error <- resid(lm(log(fcih + 1) ~ log(pro + 1) + as.factor(Source), 
                           data = bindedDF2, na.action =  na.exclude))

mapDF <- limitVar(bindedDF2, "error", 0.98)


plotAsHarvest <- ggmap(map) +
  geom_point(data = mapDF, aes(x = lon, y = lat, colour = var2)) +
  scale_colour_gradientn(
    limits = c(mapDF$minZ[1], mapDF$maxZ[1]),
    colours = matlab.like(64),
    guide = guide_colorbar(barwidth = unit(0.45, "npc"))
  ) +
  scale_x_continuous(limits = c(minX, maxX), expand = c(0, 0)) +
  scale_y_continuous(limits = c(minY, maxY), expand = c(0, 0)) +
  facet_wrap(~ Source) +
  mapTheme()


densLim <- densLimit(bindedDF2, "error", params$dpc)

plotDensity <- ggplot(data = bindedDF2) +
  geom_density(aes(x = error, color = Source), size = 1.5) +
  scale_x_continuous(limits = densLim, expand = c(0, 0))+
  densTheme() +
  labs(x = "Fuel Consumption vs. Productivity Error") +
  geom_hline(yintercept = 0, size = 2, colour = "gray")


grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(3,3,3,3,3,3),
                                   c(3,3,3,3,3,3)))

```