---
output:
  pdf_document:
    includes:
      in_header: header.tex
    fig_width: 25
    fig_height: 25
classoption: landscape
geometry: margin=2cm
params:
  pc: 0.8
  dpc: 0.98
  hFiles: NA
  sFiles: NA
  hNames: //iso19prod/IntelligentCombine/HA/ISE/reports/data/sfcVarMapping.csv
  file1: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AKFM094700-HA.csv
  file2: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AAFM094704-HA.csv
  file3: //iso19prod/IntelligentCombine/HA/ISE/reports/data/results/Kuhburg/020-1_KUHBURG_WW-1Z0S685AVFM094684-HA.csv
  path: '~/GitHub/SimToolChain/Merge/Kuhburg/WholeField/'
  file4: 020-1_KUHBURG_WW-1Z0S685AKFM094700_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file5: 020-1_KUHBURG_WW-1Z0S685AAFM094704_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file6: 020-1_KUHBURG_WW-1Z0S685AVFM094684_MPC_EP90_PerfectPredictions_min-sim_processed.csv
  file7: //iso19prod/IntelligentCombine/HA/ISE/reports/data/sfcVarMapping.csv
  tz: "Canada/Central"
---

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(comment=NA, echo=FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dbplyr)
library(tinytex)
library(colorRamps)
library(knitr)
library(kableExtra)
library(gridExtra)
library(grid)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(scales)
library(data.table)
library(pander)
source("src/compositeVersatility.R")
source("src/plotUtil.R")
source("src/tableUtil.R")

```
```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE, }
# # Read in Files
# 
# harvFiles <- params$hFiles
# i <- 1
# asHarvest <- read.csv(paste(harvFiles$path[i]), header = TRUE, as.is = TRUE)
# i <- i+1
# while(i <= length(harvFiles$path)){
#   asHarvest <- rbind(asHarvest, read.csv(paste(harvFiles$path[i]), header = TRUE, as.is = TRUE))
#   i <- i+1
# }
# 
# simFiles <- params$sFiles
# i <- 1
# simulatedHarvest <- read.csv(paste(simFiles$path[i]), header = FALSE, as.is = TRUE)
# i <- i+1
# while(i <= length(simFiles$path)){
#   simulatedHarvest <- rbind(simulatedHarvest, read.csv(paste(simFiles$path[i]), header = FALSE, as.is = TRUE))
#   i <- i+1
# }
# remove(i)
# 
# headerNames      <- read.csv(params$hNames, header = TRUE)
# names(simulatedHarvest) <- headerNames$AWS
# 
# asHarvest        <- mutate(asHarvest, Source = "As Harvested")
# simulatedHarvest <- mutate(simulatedHarvest, Source = "Simulated")
# 
# asHarvest$hwu <- with(asHarvest, ifelse(is.na(hwu), hwi, hwu))
# asHarvest[["time"]] <- NULL
# asHarvest[["Index"]] <- NULL
# bindedDF  <- rbind(asHarvest, simulatedHarvest)
```

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE, }
# Read in files
setwd(params$path)
asHarvest        <- read.csv(params$file1, header = TRUE, as.is = TRUE)
asHarvest        <- rbind(asHarvest, read.csv(params$file2, header = TRUE, as.is = TRUE))
asHarvest        <- rbind(asHarvest, read.csv(params$file3, header = TRUE, as.is = TRUE))
simulatedHarvest <- read.csv(params$file4, header = FALSE, as.is = TRUE)
simulatedHarvest <- rbind(simulatedHarvest, read.csv(params$file5, header = FALSE, as.is = TRUE))
simulatedHarvest <- rbind(simulatedHarvest, read.csv(params$file6, header = FALSE, as.is = TRUE))

headerNames      <- read.csv(params$file7, header = TRUE)
names(simulatedHarvest) <- headerNames$AWS


asHarvest        <- mutate(asHarvest, Source = "As Harvested")
simulatedHarvest <- mutate(simulatedHarvest, Source = "Simulated")
asHarvest[["time"]] <- NULL
asHarvest[["Index"]] <- NULL

# tidy the data before merging

asHarvest$hwu <- with(asHarvest, ifelse(is.na(hwu), hwi, hwu))


bindedDF  <- rbind(asHarvest, simulatedHarvest)
```

# Case Report for machine `r unique(bindedDF$serialnumber)`

```{r}

model <- bindedDF$serialnumber %>% unique(.) %>% substr(., 4, 7) %>% unique(.)

maxPower <- case_when(
  model == "S660" ~ 249,
  model == "S670" ~ 292,
  model == "S680" ~ 353,
  model == "S685" ~ 373,
  model == "S690" ~ 405,
  TRUE ~ as.numeric(NA)
)

bindedDF <- bindedDF %>%
  mutate(., pu = ep/maxPower * 100)
```

```{r}
bindedDF <- bindedDF %>% dplyr::filter(., ms == 4 | ms == 5)
```

```{r}
# Prepare separate dfs for plots
simDF <- bindedDF %>% dplyr::filter(Source == "Simulated")
harvDF <- bindedDF %>% dplyr::filter(Source == "As Harvested")
```

```{r}
# Convert GPS time to field time to prepare for Versatility Calculations

harvDF$DateTime <- with(harvDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simDF$DateTime <- with(simDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


harvDF$dateCode <-  strftime(harvDF$DateTime, format = "%Y-%m-%d" )
harvDF$hourMin <- strftime(harvDF$DateTime, format = "%Y-%m-%d-%H-%M")
simDF$dateCode <-  strftime(simDF$DateTime, format = "%Y-%m-%d" )
simDF$hourMin <- strftime(simDF$DateTime, format = "%Y-%m-%d-%H-%M")
``````{r}
# Convert GPS time to field time to prepare for Versatility Calculations

harvDF$DateTime <- with(harvDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simDF$DateTime <- with(simDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


harvDF$dateCode <-  strftime(harvDF$DateTime, format = "%Y-%m-%d" )
harvDF$hourMin <- strftime(harvDF$DateTime, format = "%Y-%m-%d-%H-%M")
simDF$dateCode <-  strftime(simDF$DateTime, format = "%Y-%m-%d" )
simDF$hourMin <- strftime(simDF$DateTime, format = "%Y-%m-%d-%H-%M")
```





```{r}

compDF <- harvDF
compDF$sessionid <- NULL
compDF$mjdoperator <- NULL
compDF$mjdorg <- NULL
compDF$mjdorgname <- NULL
compDF$sourceserialnumber <- NULL
compDF$client <- NULL
compDF$farm <- NULL
compDF$field <- NULL
compDF$serialnumber <- NULL
compDF$localtime <- NULL
compDF$region <- NULL
compDF$Source <- NULL
compDF$dateCode <- NULL
compDF <- compDF %>% dplyr::group_by(hourMin) %>% dplyr::summarise_all(funs(median))


compDF$sessionid <- harvDF$sessionid[1]
compDF$mjdoperator <- harvDF$mjdoperator[1]
compDF$mjdorg <- harvDF$mjdorg[1]
compDF$mjdorgname <- harvDF$mjdorgname[1]
compDF$sourceserialnumber <- harvDF$sourceserialnumber[1]
compDF$client <- harvDF$client[1]
compDF$farm <- harvDF$farm[1]
compDF$field <- harvDF$field[1]
compDF$serialnumber <- harvDF$Source[1]
compDF$localtime <- harvDF$localtime[1]
compDF$region <- harvDF$region[1]
compDF$Source <- harvDF$Source[1]
compDF$dateCode <- harvDF$dateCode[1]

compDF$localtime <- with(compDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simcompDF <- simDF
simcompDF$sessionid <- NULL
simcompDF$mjdoperator <- NULL
simcompDF$mjdorg <- NULL
simcompDF$mjdorgname <- NULL
simcompDF$sourceserialnumber <- NULL
simcompDF$client <- NULL
simcompDF$farm <- NULL
simcompDF$field <- NULL
simcompDF$serialnumber <- NULL
simcompDF$localtime <- NULL
simcompDF$region <- NULL
simcompDF$Source <- NULL
simcompDF$dateCode <- NULL
simcompDF <- simcompDF %>% dplyr::group_by(hourMin) %>% dplyr::summarise_all(funs(median))


simcompDF$sessionid <- simDF$sessionid[1]
simcompDF$mjdoperator <- simDF$mjdoperator[1]
simcompDF$mjdorg <- simDF$mjdorg[1]
simcompDF$mjdorgname <- simDF$mjdorgname[1]
simcompDF$sourceserialnumber <- simDF$sourceserialnumber[1]
simcompDF$client <- simDF$client[1]
simcompDF$farm <- simDF$farm[1]
simcompDF$field <- simDF$field[1]
simcompDF$serialnumber <- simDF$Source[1]
simcompDF$localtime <- simDF$localtime[1]
simcompDF$region <- simDF$region[1]
simcompDF$Source <- simDF$Source[1]
simcompDF$dateCode <- simDF$dateCode[1]

simcompDF$localtime <- with(simcompDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


compDF <- rbind(compDF, simcompDF)

bindedDFCopy <- bindedDF

bindedDF <- compDF
```

```{r, comment=NA, echo=FALSE, warning=FALSE, message=FALSE}
#Harvest Performance Scores (AKA HPS)
#  overall performance, grain productivity, power utalization, fuel Economy, grain
#  saving

hpsTable <-
  bindedDF %>% dplyr::filter(ms == 4 | ms == 5) %>% dplyr::group_by(Source) %>% dplyr::summarise(
    Performance = mean(opscore, na.rm = TRUE),
    Productivity = mean(gpscore, na.rm = TRUE),
    Power = mean(puscore, na.rm = TRUE),
    Fuel = mean(fescore, na.rm = TRUE),
    Grain = mean(glscore, na.rm = TRUE)
  )

#Harvesting Performance - Engineering Units (AKA HPEU)
# Grain Prod, Power Util, Fuel Econ, Total Loss

hpeuTable <-
  bindedDF %>%
  dplyr::filter(ms == 4 | ms == 5) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(
    GrainProd = mean(pro, na.rm = TRUE),
    PowerUtil = mean(pu, na.rm = TRUE),
    FuelEcon = mean(fcih, na.rm = TRUE)
  )

#Power Summary (AKA PS)
# Engine Harv, Eng Harv and UL, Avg Harv Specific Pwr, Propulsion Power
psTable <-
  bindedDF %>%
  dplyr::filter(ms == 4 | ms == 5 ) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(
    EngineHarv = mean(ep, na.rm = TRUE),
    EngineHarvUL = mean(ep, na.rm = TRUE),
    AvgHarvSpecificPwr = mean(ifelse(pro == 0, NA, ep/pro), na.rm = TRUE),
    PropulsionPower = mean(pp, na.rm = TRUE)
  )

engineHarvesting <- bindedDF %>%
  dplyr::filter(ms == 5) %>%
  dplyr::group_by(Source) %>%
  dplyr::summarise(EngineHarv = mean(ep, na.rm = TRUE))

psTable$EngineHarv <- engineHarvesting$EngineHarv

# agronomic and output summary (AKA AOS)
# Avg Harvest Speed, Harv Area, Avg Yield
aosTable <-
  bindedDF %>% 
  dplyr::filter(ms == 4 | ms == 5) %>% 
  dplyr::group_by(Source) %>% 
  dplyr::summarize(
    HarvestSpeed = mean(gpssp, na.rm = TRUE),
    HarvestArea = sum(gpssp * pmin(hwu, hwi, na.rm = TRUE) / 36000, na.rm = TRUE),
    AvgYield = mean(yield, na.rm = TRUE)
  )

row.names(hpsTable) <- hpsTable$Source
hpsTable$Source <- NULL
  names(hpsTable) <- c("Overall Performance", "Grain Productivity", "Power Utilization", "Fuel Economy", "Grain Saving")


row.names(hpeuTable) <- hpeuTable$Source
hpeuTable$Source <- NULL
names(hpeuTable) <- c("Grain Prod (t/h)", "Power Utl (%)", "Fuel Econ (1/t)")


row.names(psTable) <- psTable$Source
psTable$Source <- NULL
names(psTable) <- c("Engine Harv (kW)", "Eng Harv & Utl (kW)", "Avg Harv Specific Pwr (kW/t/h)", "Propulsion Power (kW)")


row.names(aosTable) <- aosTable$Source
aosTable$Source <- NULL
names(aosTable) <- c("Avg Harvest Speed (km/h)", "Harv Area (ha)", "Avg Yield (t/ha)")

```

# Overall Performance Summary

## Field Harvesting Performance Summary

### Harvesting Performance Scores

```{r, results = "asis"}
kable(round(hpsTable, digits = 0), "latex", booktabs = TRUE)
```

### Harvesting Performance - Engineering Units

```{r, results = "asis"}

kable(round(hpeuTable, digits = 1),"latex", booktabs = TRUE)
```

### Power Summary

```{r, results = "asis"}
kable(round(psTable, digits = 0), "latex", booktabs = TRUE)
```

### Agronomic & Output Summary

```{r, results = "asis"}
kable(round(aosTable, digits = 1), "latex", booktabs = TRUE)
```

```{r}
minX <- with(bindedDF, min(lon, na.rm = TRUE))
maxX <- with(bindedDF, max(lon, na.rm = TRUE))
minY <- with(bindedDF, min(lat, na.rm = TRUE))
maxY <- with(bindedDF, max(lat, na.rm = TRUE))

minX <- round(minX, 4) - 0.0001
maxX <- round(maxX, 4) + 0.0001
minY <- round(minY, 4) - 0.0001
maxY <- round(maxY, 4) + 0.0001

```

```{r}
# Calculate Zoom
bindedDFZoom <- calc_zoom(lon, lat, bindedDF) - 1

# Calculate Center of path
bindedDFlon <- (max(bindedDF$lon) + min(bindedDF$lon))/2
bindedDFlat <- (max(bindedDF$lat) + min(bindedDF$lat))/2

# Get The Maps
map <-
  get_map(location = c(lon = bindedDFlon, lat = bindedDFlat),
          zoom = bindedDFZoom, maptype = "satellite")

bindedDFscale <-
  data.frame(lat = c(min(bindedDF$lat), max(bindedDF$lat)),
             lon = c(min(bindedDF$lon), max(bindedDF$lon)))


```

## Harvesting Ground Speed (GPSSP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "gpssp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "gpssp", 
  pc = params$dpc, 
  label = "Ground Speed, kph")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Grain Productivity (PRO)

```{r}
plotAsHarvest <- plotMap(map, bindedDF, "pro", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pro", 
  pc = params$dpc, 
  label = "Grain Productivity, t/h")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Power Utilization (100 * EP/MaxPower)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "pu", params$pc)

densLim <- densLimit(bindedDF, "pu", params$dpc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pu", 
  pc = params$dpc, 
  label = "Power Utilization, %")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Consumption

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "fcih", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "fcih", 
  pc = params$dpc, 
  label = "Fuel Consumption, l/t")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))

```

## Rotor Drive Pressure (RDP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "rdp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "rdp", 
  pc = params$dpc, 
  label = "Rotor Drive Pressure, mV")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Propulsion Power (PP)

```{r}

plotAsHarvest <- plotMap(map, bindedDF, "pp", params$pc)

plotDensity <- plotDens(
  df = bindedDF, 
  item = "pp", 
  pc = params$dpc, 
  label = "Propulsion Power, kW")

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Consumption vs Grain Productivity

```{r}
yLim <- densLimit(bindedDF, "fcih", params$dpc)
xLim <- densLimit(bindedDF, "pro", params$dpc)

ggplot(data = bindedDF, aes(x = pro, y = fcih, color = Source), size = 2) +
  scale_x_continuous(limits = c(xLim$minZ[1], xLim$maxZ[1]), expand = c(0, 0)) +
  scale_y_continuous(limits = c(yLim$minZ[1], yLim$maxZ[1]), expand = c(0, 0)) +
  geom_point( alpha=0.35) +
  stat_density_2d(size = 1, contour = TRUE) +
  onePlot() +
  labs(x = "Grain Productivity, t/h", y = "Fuel Consumption, l/t")
```

## Overall Performance (OPSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "opscore", 
                         pc = params$pc, 
                         score = TRUE)
  
plotDensity <- plotDens(df = bindedDF, 
                        item = "opscore",
                        pc = params$dpc,
                        label = "Overall Performance Score",
                        score = TRUE) 


grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Grain Productivity (GPSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "gpscore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "gpscore",
                        pc = params$dpc,
                        label = "Grain Productivity Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Power Utilization Score (PUSCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "puscore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "puscore",
                        pc = params$dpc,
                        label = "Power Utilization Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```

## Fuel Economy Score (FESCORE)

```{r}

plotAsHarvest <- plotMap(map = map, 
                         df = bindedDF, 
                         item = "fescore", 
                         pc = params$pc, 
                         score = TRUE)

plotDensity <- plotDens(df = bindedDF, 
                        item = "fescore",
                        pc = params$dpc,
                        label = "Fuel Economy Score",
                        score = TRUE) 

grid.arrange(plotAsHarvest,
             plotDensity,
             layout_matrix = rbind(c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(1,1,1,1,1,1),
                                   c(2,2,2,2,2,2),
                                   c(2,2,2,2,2,2)))
```


```{r}
# Convert GPS time to field time to prepare for Versatility Calculations

harvDF$DateTime <- with(harvDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simDF$DateTime <- with(simDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


harvDF$dateCode <-  strftime(harvDF$DateTime, format = "%Y-%m-%d" )
harvDF$hourMin <- strftime(harvDF$DateTime, format = "%Y-%m-%d-%H-%M")
simDF$dateCode <-  strftime(simDF$DateTime, format = "%Y-%m-%d" )
simDF$hourMin <- strftime(simDF$DateTime, format = "%Y-%m-%d-%H-%M")
``````{r}
# Convert GPS time to field time to prepare for Versatility Calculations

harvDF$DateTime <- with(harvDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simDF$DateTime <- with(simDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


harvDF$dateCode <-  strftime(harvDF$DateTime, format = "%Y-%m-%d" )
harvDF$hourMin <- strftime(harvDF$DateTime, format = "%Y-%m-%d-%H-%M")
simDF$dateCode <-  strftime(simDF$DateTime, format = "%Y-%m-%d" )
simDF$hourMin <- strftime(simDF$DateTime, format = "%Y-%m-%d-%H-%M")
```





```{r}

compDF <- harvDF
compDF$sessionid <- NULL
compDF$mjdoperator <- NULL
compDF$mjdorg <- NULL
compDF$mjdorgname <- NULL
compDF$sourceserialnumber <- NULL
compDF$client <- NULL
compDF$farm <- NULL
compDF$field <- NULL
compDF$serialnumber <- NULL
compDF$localtime <- NULL
compDF$region <- NULL
compDF$Source <- NULL
compDF$dateCode <- NULL
compDF <- compDF %>% dplyr::group_by(hourMin) %>% dplyr::summarise_all(funs(median))


compDF$sessionid <- harvDF$sessionid[1]
compDF$mjdoperator <- harvDF$mjdoperator[1]
compDF$mjdorg <- harvDF$mjdorg[1]
compDF$mjdorgname <- harvDF$mjdorgname[1]
compDF$sourceserialnumber <- harvDF$sourceserialnumber[1]
compDF$client <- harvDF$client[1]
compDF$farm <- harvDF$farm[1]
compDF$field <- harvDF$field[1]
compDF$serialnumber <- harvDF$Source[1]
compDF$localtime <- harvDF$localtime[1]
compDF$region <- harvDF$region[1]
compDF$Source <- harvDF$Source[1]
compDF$dateCode <- harvDF$dateCode[1]

compDF$localtime <- with(compDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)

simcompDF <- simDF
simcompDF$sessionid <- NULL
simcompDF$mjdoperator <- NULL
simcompDF$mjdorg <- NULL
simcompDF$mjdorgname <- NULL
simcompDF$sourceserialnumber <- NULL
simcompDF$client <- NULL
simcompDF$farm <- NULL
simcompDF$field <- NULL
simcompDF$serialnumber <- NULL
simcompDF$localtime <- NULL
simcompDF$region <- NULL
simcompDF$Source <- NULL
simcompDF$dateCode <- NULL
simcompDF <- simcompDF %>% dplyr::group_by(hourMin) %>% dplyr::summarise_all(funs(median))


simcompDF$sessionid <- simDF$sessionid[1]
simcompDF$mjdoperator <- simDF$mjdoperator[1]
simcompDF$mjdorg <- simDF$mjdorg[1]
simcompDF$mjdorgname <- simDF$mjdorgname[1]
simcompDF$sourceserialnumber <- simDF$sourceserialnumber[1]
simcompDF$client <- simDF$client[1]
simcompDF$farm <- simDF$farm[1]
simcompDF$field <- simDF$field[1]
simcompDF$serialnumber <- simDF$Source[1]
simcompDF$localtime <- simDF$localtime[1]
simcompDF$region <- simDF$region[1]
simcompDF$Source <- simDF$Source[1]
simcompDF$dateCode <- simDF$dateCode[1]

simcompDF$localtime <- with(simcompDF,
  .POSIXct(ISOdatetime(gpsy, gpsm, gpsd, gpsh, gpsmi, gpss, tz = "UTC"), tz = params$tz)
)


compDF <- rbind(compDF, simcompDF)
```



```{r title, results='asis', fig.width=8, fig.height=3}
# The following are versatility table output and time vs metric plotting
# The for-loops are used to create versatility pages for each unique date

for( i in unique(harvDF$dateCode)){
  cat("\\pagebreak")
  
  VersDF <- compDF %>% 
    dplyr::filter(., dateCode == i)
  VersDF$time <- VersDF$localtime
  VersDF$model_year <- unique(substr(asHarvest$serialnumber, 10, 10))
  VersDF$model <- unique(substr(asHarvest$serialnumber, 4, 7))
  VersDF$machine_name <- VersDF$Source
  
  p1 <- ggplot(VersDF, aes(x = DateTime, y = pro, colour = Source)) +
    geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
    coord_cartesian(ylim=c(0, 100) + c(0,1)) +
    timeTheme() +
    labs(x = "Time", y = "Grain Productivity, t/h")
  
  # pandoc.header(paste("Grain Productivity", i, sep = " "), level=2)
  
  vtab <- get_versatility_tbl(unique(asHarvest$field)[1], "pro", VersDF)
  
  print(p1)
  
  cat(vtab[1], "\n")
  cat(vtab[2], "\n")
  
  
  
}

for( i in unique(harvDF$dateCode)){
  cat("\\pagebreak")

   VersDF <- compDF %>% 
    dplyr::filter(., dateCode == i)
  VersDF$time <- VersDF$DateTime
  VersDF$model_year <- unique(substr(asHarvest$serialnumber, 10, 10))
  VersDF$model <- unique(substr(asHarvest$serialnumber, 4, 7))
  VersDF$machine_name <- VersDF$Source

  p1 <- ggplot(VersDF, aes(x = DateTime, y = gpscore, colour = Source)) +
    geom_smooth( method = "loess", method.args = list(degree = 2), size = 1.75, se = FALSE, span = 0.33) +
    coord_cartesian(ylim=c(0, 100) + c(0,1)) +
    timeTheme() +
    labs(x = "Time", y = "Grain Productivity Score")
  # pandoc.header(paste("As Harvest Grain Productivity Score", i, sep = " "), level=2)
  vtab <- get_versatility_tbl(unique(asHarvest$field)[1], "gpscore", VersDF)

  print(p1)

  cat(vtab[1], "\n")
  cat(vtab[2], "\n")


  cat("\\pagebreak")


}
```